Analysis of cloud enhancement events in a 30-year record of global solar irradiance at Thessaloniki, Greece

### 2024-09-07 article/article.Rmd
Commit 2024-09-07 21:12

```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
knitr::include_graphics("../images/P-CS-change-1.png")
```

@@

\begin{equation}
\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
\end{equation}
where $y$ the date as a decimal fraction of the year

@@

An example of the identification of CE events for a selected day is given in the
Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
reference irradiance and the CE and ECE identification thresholds are shown along
with the actual GHI measurements.  In addition, we provide an example scatter plot
between the measured and the modeled cloud-free irradiance for one year, where the CE
and ECE events are clearly grouped above the threshold of irradiance
(Figure\nobreakspace{}\ref{fig:example-year}).

>>>>

<!--
```{r CS-change, echo=FALSE, fig.cap="Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023."}
knitr::include_graphics("../images/P-CS-change-1.png")
```
-->

@@

\begin{equation}
\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
\end{equation}
where $y$ the date as a decimal fraction of the year. For the period of the study the
relative change of AOD ranges between $-1.88$ and $-0.23\,\%$.

@@

An example of the identification of CE events for a selected day is given in the
Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the cloud-free
reference irradiance and the CE and ECE thresholds are shown along with the actual
GHI measurements.  The GHI data in the periods 7:30 -- 8:30 and after 14:00 are very
close to the modeled cloud-free GHI (light blue line) thus were identified as
cloud-free instances. There is some ambiguity for the data points laying between the
CE threshold and the cloud-free irradiance, which are not identified as CE events.
These data points correspond to cases either with AOD below the one assumed in the
model, or with very small OI.

In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year} an example
scatter plot between the measured GHI and the modeled cloud-free irradiance for one
year (2005), where the CE and ECE events are clearly grouped above the cloud-free
irradiance (approximated with the green line).

### 2024-09-07 article/article.tex
Commit 2024-09-07 21:12

{\centering \includegraphics[width=1\linewidth]{../images/P-CS-change-1}

\caption{Simulated long-term change in cloud-free irradiance relative to the climatological values due to changes in AOD in Thessaloniki for the period 1994 -- 2023.}\label{fig:CS-change}
\end{figure}

\begin{equation}
\Delta(\text{AOD}) = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 [\%] \label{eq:AODchange}
\end{equation} where \(y\) the date as a decimal fraction of the year

@@

To assess the validity of the threshold, we tested the correlation of
the measured GHI with those of the cloud-free irradiance (Figure), for
only cloud-free measurements of days with data availability of greater
than 80\%. Due to the selection of the simulations with lower AOD and
WC, these values have a positive bias of more than (Correlation). This
was desired so that together with the PSE criterion, we could achieve a
clear distinction of PSE cases.

@@

An example of the identification of CE events for a selected day is
given in the Figure\nobreakspace{}\ref{fig:example-day}, where the daily
course of the cloud-free reference irradiance and the CE and ECE
identification thresholds are shown along with the actual GHI
measurements. In addition, we provide an example scatter plot between
the measured and the modeled cloud-free irradiance for one year, where
the CE and ECE events are clearly grouped above the threshold of
irradiance (Figure\nobreakspace{}\ref{fig:example-year}).

>>>>

\begin{equation}
\Delta(\text{AOD}) [\%] = -12170 + 12.05 \cdot y + -0.002981 \cdot y^2 \label{eq:AODchange}
\end{equation} where \(y\) the date as a decimal fraction of the year.
For the period of the study the relative change of AOD ranges between
\(-1.88\) and \(-0.23\,\%\).

@@

To assess the validity of the threshold, we tested the correlation of
the measured GHI with those of the cloud-free irradiance
(Figure\nobreakspace{}\ref{fig:validation-GHI}), for only cloud-free
measurements of days with data availability of greater than 80\%. Due to
the selection of the simulations with lower AOD and WC, these values
have a positive bias of more than \(18\,\text{W}/\text{m}^2\). This bias
was desired, so that together with the CE criterion, could achieve a
clear distinction of CE cases.

{\centering \includegraphics[width=1\linewidth]{../images/P-validation-cloudfree-GHI-1}

\caption{The reference green line goes through the origin with a slope of one.}\label{fig:validation-GHI}
\end{figure}

@@

An example of the identification of CE events for a selected day is
given in the Figure\nobreakspace{}\ref{fig:example-day}, where the daily
course of the cloud-free reference irradiance and the CE and ECE
thresholds are shown along with the actual GHI measurements. The GHI
data in the periods 7:30 -- 8:30 and after 14:00 are very close to the
modeled cloud-free GHI (light blue line) thus were identified as
cloud-free instances. There is some ambiguity for the data points laying
between the CE threshold and the cloud-free irradiance, which are not
identified as CE events. These data points correspond to cases either
with AOD below the one assumed in the model, or with very small OI.

In addition, we provide in Figure\nobreakspace{}\ref{fig:example-year}
an example scatter plot between the measured GHI and the modeled
cloud-free irradiance for one year (2005), where the CE and ECE events
are clearly grouped above the cloud-free irradiance (approximated with
the green line). (Figure\nobreakspace{}\ref{fig:example-year}).
